EvoSuite at the SBST 2017 Tool Competition

### 2017-02-18 papers/sbst17/paper_sbst17.tex
Update scripts and add some tables

% \begin{table*}[t]
%   \centering
%   \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
% \resizebox{0.9\textwidth}{!}{  
% \input{mainTable.tex}
% }	
% \end{table*}

\begin{table*}[t]
  \centering
  \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.8\textwidth}{!}{  
%\input{coverageTable.tex}
}
\end{table*}

\begin{table*}[t]
  \centering
  \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{0.8\textwidth}{!}{  
%\input{faultTable.tex}
}	
\end{table*}

>>>>

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the SBST benchmark classes.}
\resizebox{\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}

% \begin{table*}[t]
%   \centering
%   \caption{\label{table:coverage_results}Detailed coverage results of \EVOSUITE on the SBST benchmark classes.}
% \resizebox{0.8\textwidth}{!}{  
% \input{coverageTable.tex}
% }
% \end{table*}

% \begin{table*}[t]
%   \centering
%   \caption{\label{table:fault_results}Detailed fault detection results of \EVOSUITE on the SBST benchmark classes.}
% \resizebox{0.8\textwidth}{!}{  
% \input{faultTable.tex}
% }	
% \end{table*}
